Stochastic Variance-Reduced Policy Gradient

### 2018-06-27 poster/poster.tex
edited central column

\colorlet{redp}{red!20} % vert S
\colorlet{greenp}{vert3!20} % vert S\usepackage[framemethod=tikz]{mdframed}
\colorlet{bluep}{blue!20} % vert S
\colorlet{blueg}{blue!70!green!90!white}

\newcommand{\hl}[3][\fboxsep1pt]{{#1\colorbox{#2}{#3}}}%
%\newcommand{\hl}[2]{{\adjustbox{bgcolor=#1}{#2}}}%

\newcommand{\hlr}[1]{\hl{redp}{#1}}
\newcommand{\hlg}[1]{\hl{greenp}{#1}}
\newcommand{\hlb}[1]{\hl{bluep}{#1}}
\newcommand{\hlo}[1]{\hl{orange!50}{#1}}
\newcommand{\hly}[1]{\hl{yellow!70!black!50!white}{#1}}
\newcommand{\hlblg}[1]{\hl{blue!75!green!20!white}{#1}}
\newcommand{\tikzhlblg}[1]{\tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=blue!75!green!20!white]{{#1}};}}
\newcommand{\tikzhly}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=yellow!70!black!50!white]{{#1}};}}
\newcommand{\tikzhlr}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=redp]{{#1}};}}
\newcommand{\tikzhlg}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=greenp]{{#1}};}}
\newcommand{\tikzhlb}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=bluep]{{#1}};}}

@@

\usepackage{tcolorbox}

@@

\usepackage{tabu}

@@

@@

    \begin{minipage}{.85\textwidth}
    \noindent \hly{Sample efficiency} is crucial in Reinforcement Learning (RL), where collecting samples is extremely expensive\\ 
    \hspace*{.3cm} $\implies$ \textbf{FG} often \underline{unfeasible}

	\vspace{2mm}
	\noindent Slower convergence of \textbf{SG} due to high \hly{gradient variance}.
    \end{minipage}

    \vspace{.3cm}
    \noindent $\blacktriangleright$~ \hlr{Solution:} from finite-sum optimization in Supervise Learning:
	\begin{itemize}\compresslist
		\item \textbf{Stochastic Variance-Reduced Gradient (SVRG)} $\longrightarrow O(N+\nicefrac{N^{\nicefrac{2}{3}}}{\epsilon})$
	\end{itemize}
}

@@

\headerbox{What is out there?}{name=related,column=0,row=1, span=1,below=problem,above=bottom}{
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \noindent From the \hlb{\textbf{SL}} literature, \textit{separate} study of: 
	\begin{itemize}\compresslist
		\item \chall{Non-concavity}~\citep{du2017svrgpe,reddi2016stochastic}
		\item \chall{Infinite dataset}~\citep{harikandeh2015stopwasting,bietti2017stochastic}
	\end{itemize}

    \noindent From the \hlb{\textbf{RL}} literature:
	\begin{itemize}\compresslist
		\item \textbf{SVRPGE}~\citep{du2017svrgpe}: SVRG for policy \textit{evaluation}
		\item \textbf{SVRPO}~\citep{xu2017svrgtrpo}: direct application of SVRG to TRPO
	\end{itemize}

@@

\noindent\begin{minipage}[t]{.32\textwidth}
        \hlg{The easy part:}\\[.2cm]
%\begin{itemize}\compresslist
        $\bullet$~Take any \textbf{unbiased} policy gradient estimator $g(\tau|\vtheta)$ (\eg REINFORCE)\\[.15cm]
    $\bullet$~\textbf{SVRG} idea: combine \hly{frequent \textbf{SG}} with \hly{rare \textbf{FG}} into a corrected gradient estimator $\gradBlack{\vtheta}$\\[.15cm]
    $\bullet$~Two-time scales:\\ \hspace*{.8cm} $1$ \textbf{epoch} $=m$ \textbf{iterations}
%\end{itemize}
\end{minipage}
\hfill%
\begin{minipage}[t]{.33\textwidth}
        \hlo{Solving the RL challenges:}\\[.2cm]
%\begin{enumerate}\compresslist
    $\bullet$~Manage \chall{non-concavity} with \textbf{smooth} policies (\eg Gaussian)\\[.15cm]
    $\bullet$~Approximate \chall{infinite dataset} with a large \textbf{batch size} $N$\\[.15cm]
	$\bullet$~Correct \chall{nonstationarity} with \textbf{importance weighting}	
%\end{enumerate}
\end{minipage}
\hfill%
\begin{minipage}[t]{.31\textwidth}
        \vspace*{-.4cm}
        \hspace*{1.8cm} \emph{Algorithm}
        \vspace*{-.2cm}
        \bookboxx{
                \small
                \textbf{For} $s = 1,\ldots$\\
                \hspace*{.2cm} Sample $N$ trajectories using $\theta^s$\\
                \hspace*{.2cm} Compute FG $\wh{\nabla}_N J(\theta^S)$\\
                \hspace*{.2cm} \textbf{For} $t = 1, \ldots, m-1$\\
                \hspace*{.4cm} Sample $B$ trajectories using $\theta^{s+1}_t$\\
                \hspace*{.4cm} Compute SG $\wh{\nabla}_B J(\theta^{s+1}_t)$ and \\
                \hspace*{.6cm} $c_t^{s+1} = \omega(\theta^{s+1}_t, \theta^s)\wh{\nabla}_B J(\theta^{s+1}_t)$\\
                \hspace*{.4cm} Compute $\theta^{s+1}_{t+1}$ using $\gradBlack{\theta^{s+1}_t}$
        }
\end{minipage}

@@

\noindent\dotfill
\begin{tabu} to \textwidth{X[c]X[2c]X[c]}
	\multirow{2}{*}{
		\shortstack{
                \tikz[baseline]{\node[anchor=base,fill=greenp, inner sep=2pt](FGtext){$\textbf{FG term}$};}\\
			$\frac{1}{N}\sum_{i=1}^{N} g(\tau_i|\wt{\vtheta})$\\
			$\tau_i\sim\wt{\vtheta}$\\
			$N$ trajectories\\
			Accurate but \bad{expensive}\\
			$\downarrow$\\
			Updated once per \textbf{epoch}
		}
	}	 
	&\tikz[overlay]{ 
    \node[inner sep=5pt, xshift=-.2cm]{\large{$\gradBlack{\vtheta} := \tikz[baseline]{\node[anchor=base, fill=greenp](FG){$\wh{\nabla}_N J(\wt{\vtheta})$};} + 
            \tikz[baseline]{\node[anchor=base, fill=redp](SG){$\wh{\nabla}_B J({\vtheta})$};} - 
    \tikz[baseline]{\node[anchor=base, fill=yellow](C){$\omega(\vtheta, \wt{\vtheta}) \wh{\nabla}_B J({\wt{\vtheta}})$};}$}
		};
	}  
	\vspace{0.9cm} 
	& \multirow{2}{*}{
		\shortstack{
            \tikz[baseline]{\node[anchor=base, fill=yellow, inner sep=2pt](Ctext){$\textbf{Correction term}$};}\\
			$\frac{1}{B}\sum_{i=1}^{B}\underbrace{\omega(\tau_i|\vtheta,\wt{\vtheta})}_{\textbf{imp. weight}}g(\tau_i|\wt{\vtheta})$\\
			Trajectories from SG term \\
			Ensures SVRG properties\\
			\bad{Distribution mismatch}\\
			$\downarrow$\\
			\textbf{importance weighting}\\
			$\downarrow$\\
			\bad{new source of variance}
		}
	} \\
	& \shortstack{
    \tikz[baseline]{\node[anchor=base, fill=redp, inner sep=2pt](SGtext){$\textbf{SG term}$};}\\
		$\frac{1}{B}\sum_{i=1}^{B} g(\tau_i|\vtheta)$\\
		$\tau_i\sim\vtheta$\\
		$B<<N$ trajectories\\
		Computed at each iteration\\
		\\Cheap but \bad{high-variance}\\
		$\downarrow$\\
		Stabilized by other terms
	}
\end{tabu}
\tikz[overlay]{
        \path[->, greenp, thick] (FG.north west) edge[bend right] (FGtext.east);
        \path[->, yellow, thick] (C.east) edge[bend left] (Ctext.west);
        \draw[->, redp, thick] (SG.south) -- (SGtext.north);
}

\vspace{0.5cm}

\begin{minipage}[t]{.55\textwidth}
	Fundamental \textbf{SVRG} properties:
	\begin{enumerate}
            \item \textcolor{myblue}{\textbf{Unbiasedness:}} $\EVV[]{\gradBlack{\vtheta}} = \gradJ{\vtheta}$
            \item \textcolor{myblue}{\textbf{Vanishing variance:}} $\Var{\gradBlack{\vtheta}}\to0$ as $\vtheta\to\vtheta^*$
	\end{enumerate}
\vfill
\end{minipage}
\hfill%
\begin{minipage}[t]{.4\textwidth}
        \hly{\textbf{Importance weighting}}

Use samples from $\vtheta$ as taken with $\wt{\vtheta}$:
\vspace{-0.2cm}
\begin{equation*}
	w(\tau|\vtheta,\wt{\vtheta}) = \frac{p(\tau|\wt\vtheta)}{p(\tau|\vtheta)}
	\quad
	\genfrac{}{}{0pt}{}{\leftarrow \textit{target distribution}}
		{\leftarrow \textit{source distribution}}
\end{equation*}
\end{minipage}
}

\headerbox{Convergence}{name=convergence,column=1,span=2,row=2, below=svrpg, above=bottom}{
\begin{align*}
&\EVV[]
{\norm[2]{\nabla J(\vtheta_A)}^2} 
\leq
\frac{J(\vtheta^*)-J(\vtheta_0)}{\psi T} +
\frac{\zeta}{N}
+\frac{\xi}{B},
\end{align*}

Serve piu' spazio, ma l'organizzazione del box sopra e' tutta da vedere. Mancano anche le due basic properties
}

\headerbox{Heuristics}{name=heuristics,column=3,span=1,row=0,height=0.5,height=0.32}{
	\begin{itemize}
		\item Adaptive step size
		\item Adaptive epoch size
		\item Normalized Importance Weighting
		\item Critic (baseline)
	\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Empirical Results}{name=emp,column=3,row=1,span=1,below=heuristics,height=0.45}{
	Direi che ci stanno 2 grafici, ma devo pensare a quali mettere

@@

\headerbox{References}{name=ref,column=3,row=1,span=1,below=emp,above=bottom}{
        \tiny
\bibliographystyle{plainnat}
\begingroup
\renewcommand{\section}[2]{}%
\bibliography{../svrpg.bib}
\endgroup
}

>>>>

\colorlet{redp}{red!20} % vert S
\colorlet{greenp}{vert3!20} % vert S\usepackage[framemethod=tikz]{mdframed}
\colorlet{bluep}{blue!12} % vert S
\colorlet{blueg}{blue!70!green!90!white}
\definecolor{yellowp}{rgb}{0.99, 0.99, 0.59}
\colorlet{orangep}{orange!40}
\newcommand{\hl}[3][\fboxsep1pt]{{#1\colorbox{#2}{#3}}}%
%\newcommand{\hl}[2]{{\adjustbox{bgcolor=#1}{#2}}}%

\newcommand{\hlr}[1]{\hl{redp}{#1}}
\newcommand{\hlg}[1]{\hl{greenp}{#1}}
\newcommand{\hlb}[1]{\hl{bluep}{#1}}
\newcommand{\hlo}[1]{\hl{orangep}{#1}}
\newcommand{\hly}[1]{\hl{yellow!70!black!40!white}{#1}}
\newcommand{\hlblg}[1]{\hl{blue!75!green!20!white}{#1}}
\newcommand{\tikzhlblg}[1]{\tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=blue!75!green!20!white]{{#1}};}}
\newcommand{\tikzhly}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=yellow!70!black!50!white]{{#1}};}}
\newcommand{\tikzhlr}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=redp]{{#1}};}}
\newcommand{\tikzhlg}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=greenp]{{#1}};}}
\newcommand{\tikzhlb}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=bluep]{{#1}};}}

@@

%\usepackage{tcolorbox}

@@

\usepackage{tabu}
\usepackage{schemata}

@@

%Reduce linespace in biblio
\setlength{\bibsep}{2pt}

\usepackage[many]{tcolorbox}
\usetikzlibrary{decorations.pathreplacing}
%\tcbset{%
%	enhanced,
%	coltitle=black, 
%	detach title,
%	left=10mm,
%	overlay={
%		\node[rotate=90, minimum width=1cm, anchor=south,yshift=-0.8cm] at (frame.east) {\tcbtitle};
%	}
%}
\newtcolorbox{rightbrace1}{%
	boxsep=0cm,
	left=.05cm,
	top=.05cm,
	bottom=.05cm,
	grow to left by=-.35cm,
	colback=black!10,
	enhanced jigsaw, 
	breakable, % allow page breaks
	frame hidden, % hide the default frame
	width=6.1cm,
	overlay={%
		\draw [
		fill=none, % fill paper
		decoration={brace,amplitude=0.5em},
		decorate,
		ultra thick,
		darkgray,
		]
		% right line
		(frame.north east)--(frame.south east);
		\node[rotate=270, minimum width=1cm, anchor=south,yshift=0.35cm] at (frame.east) {iteration};
	},
	% paragraph skips obeyed within tcolorbox
	parbox=false,
}
%
\newtcolorbox{rightbrace2}{%
	boxsep=0cm,
	left=.05cm,
	top=.05cm,
	bottom=.05cm,
	grow to left by=-.35cm,
	colback=black!5!white,
	enhanced jigsaw, 
	breakable, % allow page breaks
	frame hidden, % hide the default frame
	width=7.6cm,
	overlay={%
		\draw [
		fill=none, % fill paper
		decoration={brace,amplitude=0.5em},
		decorate,
		ultra thick,
		darkgray,
		]
		% right line
		(frame.north east)--(frame.south east);
		\node[rotate=270, minimum width=1cm, anchor=south,yshift=0.3cm] at (frame.east) {epoch};
	},
	% paragraph skips obeyed within tcolorbox
	parbox=false,
}

@@

    \begin{minipage}{.85\textwidth}
    \noindent \hlr{Sample efficiency} is crucial in Reinforcement Learning (RL), where collecting samples is extremely expensive\\ 
    \hspace*{.3cm} $\implies$ \textbf{FG} often \underline{unfeasible}

	\vspace{2mm}
	\noindent Slower convergence of \textbf{SG} due to high \hlr{gradient variance}.
    \end{minipage}

    \vspace{.3cm}
    \noindent $\blacktriangleright$~ \hly{Solution} from finite-sum optimization in Supervised Learning (SL):
	\begin{itemize}\compresslist
		\item \textbf{Stochastic Variance-Reduced Gradient (SVRG)} $\longrightarrow O(N+\nicefrac{N^{\nicefrac{2}{3}}}{\epsilon})$
	\end{itemize}
}

@@

\headerbox{What is out there?}{name=related,column=0,row=1, span=1,below=problem,above=bottom}{
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \noindent From the \hlb{\textbf{SL}} literature, \textit{separate} study of: 
	\begin{itemize}\compresslist
		\item \chall{Non-concavity}~\citep{allen2016variance,reddi2016stochastic}
		\item \chall{Infinite dataset}~\citep{harikandeh2015stopwasting,bietti2017stochastic}
	\end{itemize}

    \noindent From the \hlb{\textbf{RL}} literature:
	\begin{itemize}\compresslist
		\item \textbf{SVRPGE}~\citep{du2017svrgpe}: policy \textit{evaluation}
		\item \textbf{SVRPO}~\citep{xu2017svrgtrpo}: direct application of SVRG to TRPO
	\end{itemize}

@@

\noindent\begin{minipage}[t]{.48\textwidth}
\begin{tcolorbox}[left=0cm,right=0cm,top=0cm,bottom=0cm,colback=white, boxsep=.1cm, colframe=yellow!70!black!40!white, grow to left by=0cm, grow to right by=0cm]
\vspace*{-.11cm}\hspace*{-.11cm}\hlb{The easy part:}\\[.2cm]
%\begin{itemize}\compresslist
        $\bullet$~Take any \textbf{unbiased} policy gradient estimator $g(\tau|\vtheta)$ (\eg REINFORCE)\\[.15cm]
    $\bullet$~\textbf{SVRG} idea: combine \hlr{frequent \textbf{SG}} with \\\hlg{rare \textbf{FG}} into a corrected gradient estimator $\gradBlack{\vtheta}$\\[.15cm]
    $\bullet$~Two-time scales: $1$ \textbf{epoch} $=m$ \textbf{iterations}
%\end{itemize}
\end{tcolorbox}
\end{minipage}\hfill%
\begin{minipage}[t]{.48\textwidth}
\begin{tcolorbox}[left=0cm,right=0cm,top=0cm,bottom=0cm,colback=white, boxsep=.1cm, colframe=orangep, grow to left by=0cm, grow to right by=0cm]
\vspace*{-.11cm}\hspace*{-.11cm}\hlo{Solving the RL challenges:}\\[.2cm]
%\begin{enumerate}\compresslist
    $\bullet$~Manage \chall{non-concavity} with \textbf{smooth} policies (\eg Gaussian)\\[.15cm]
    $\bullet$~Approximate \chall{infinite dataset} with a large \textbf{batch size} $N$\\[.15cm]
	$\bullet$~Correct \chall{nonstationarity} with \textbf{importance weighting}	
%\end{enumerate}
\end{tcolorbox}
\end{minipage}

@@

\noindent\dotfill
\begin{tabu} to \textwidth{X[c]X[2c]X[c]}
	\multirow{2}{*}{
		\shortstack{
                \tikz[baseline]{\node[anchor=base,fill=greenp, inner sep=2pt](FGtext){$\textbf{FG term}$};}\\
			$\frac{1}{N}\sum_{i=1}^{N} g(\tau_i|\wt{\vtheta})$\\
			$\tau_i\sim\wt{\vtheta}$\\
			$N$ trajectories\\
			Accurate but \bad{expensive}\\
			$\downarrow$\\
			Updated once per \textbf{epoch}
		}
	}	 
	&\tikz[overlay]{ 
    \node[inner sep=5pt, xshift=-.2cm]{\large{$\gradBlack{\vtheta} := \tikz[baseline]{\node[anchor=base, fill=greenp](FG){$\wh{\nabla}_N J(\wt{\vtheta})$};} + 
            \tikz[baseline]{\node[anchor=base, fill=redp](SG){$\wh{\nabla}_B J({\vtheta})$};} - 
    \tikz[baseline]{\node[anchor=base, fill=yellowp](C){$\omega(\vtheta, \wt{\vtheta}) \wh{\nabla}_B J({\wt{\vtheta}})$};}$}
		};
	}  
	\vspace{0.9cm} 
	& \multirow{2}{*}{
		\shortstack{
            \tikz[baseline]{\node[anchor=base, fill=yellowp, inner sep=2pt](Ctext){$\textbf{Correction term}$};}\\
			$\frac{1}{B}\sum_{i=1}^{B}\underbrace{\omega(\tau_i|\vtheta,\wt{\vtheta})}_{\textbf{imp. weight}}g(\tau_i|\wt{\vtheta})$\\
			Trajectories from SG term \\
			Ensures SVRG properties\\
			\bad{Distribution mismatch}\\
			$\downarrow$\\
			\textbf{importance weighting}\\
			$\downarrow$\\
			\bad{new source of variance}
		}
	} \\
	& \shortstack{
    \tikz[baseline]{\node[anchor=base, fill=redp, inner sep=2pt](SGtext){$\textbf{SG term}$};}\\
		$\frac{1}{B}\sum_{i=1}^{B} g(\tau_i|\vtheta)$\\
		$\tau_i\sim\vtheta$\\
		$B<<N$ trajectories\\
		Computed at each iteration\\
		\\Cheap but \bad{high-variance}\\
		$\downarrow$\\
		Stabilized by other terms
	}
\end{tabu}
\tikz[overlay]{
        \path[->, greenp, thick] (FG.north west) edge[bend right] (FGtext.east);
        \path[->, yellowp, thick] (C.east) edge[bend left] (Ctext.west);
        \draw[->, redp, thick] (SG.south) -- (SGtext.north);
}

\vspace{0.2cm}
\noindent
\begin{minipage}[t]{.48\textwidth}
	\begin{tcolorbox}[left=0cm,right=0cm,top=0cm,bottom=0cm,colback=white, boxsep=.1cm, colframe=bluep, grow to left by=0cm, grow to right by=0cm]
		\vspace*{-.11cm}\hspace*{-.2cm}
		\hlb{Fundamental SVRG properties:}

	\begin{enumerate}
	\item \textcolor{myblue}{\textbf{Unbiasedness:}} $\EVV[]{\gradBlack{\vtheta}} = \gradJ{\vtheta}$
	\item \textcolor{myblue}{\textbf{Vanishing variance:}} $\Var{\gradBlack{\vtheta}}\to0\:\:$ as $\:\:\vtheta\to\vtheta^*$
	\end{enumerate}
	\end{tcolorbox}
\end{minipage}
\hfill%
\begin{minipage}[t]{.48\textwidth}
\begin{tcolorbox}[left=0cm,right=0cm,top=0cm,bottom=0cm,colback=white, boxsep=.1cm, colframe=yellow!70!black!40!white, grow to left by=0cm, grow to right by=0cm]
\vspace*{-.11cm}\hspace*{-.2cm}
\hly{Importance weighting}

Use samples from $\vtheta$ as taken with $\wt{\vtheta}$:
\vspace{-0.2cm}
\begin{equation*}
	w(\tau|\vtheta,\wt{\vtheta}) = \frac{p(\tau|\wt\vtheta)}{p(\tau|\vtheta)}
	\quad
	\genfrac{}{}{0pt}{}{\leftarrow \textit{target distribution}}
		{\leftarrow \textit{source distribution}}
\end{equation*}
\end{tcolorbox}
\end{minipage}
}

\headerbox{Convergence}{name=convergence,column=2,span=1,row=2, below=svrpg, above=bottom}{
\noindent
\chall{Non-concavity }$\longrightarrow$\textit{ local} maximum

\noindent\hlb{Linear} rate under increasing batch sizes:
\begin{align*}
&\EVV[]
{\norm[]{\nabla J(\vtheta)}^2} \leq
\tikz[baseline]{\node[anchor=base, fill=bluep,inner sep=5](Nterm){$\frac{J(\vtheta^*)-J(\vtheta_0)}{\psi T}$};}
+
\tikz[baseline]{\node[anchor=base, fill=orangep,inner sep=5](Nterm){$\frac{\zeta}{N}$};} + 
\tikz[baseline]{\node[anchor=base, fill=orangep,inner sep=5](Bterm){$\frac{\xi}{B}$};}
\end{align*}

\vspace*{1cm}

\noindent
\begin{tabular}{cc}
\shortstack{ \tikz[baseline]{\node[anchor=base, inner sep=2](Ntext){\chall{Infinite-dataset} error};}\\ 
from FG approximation\\
$\downarrow$ 
\\take \textit{large} $N$
}&
\hfill%
\shortstack{
\vspace*{-.1cm}
\tikz[baseline]{\node[anchor=base, inner sep=2](Btext){\chall{Non-stationarity} error};}\\ 
from importance weighting\\
	$\downarrow$ 
	\\take \textit{large} $B$ (still $<<N$)
}
\end{tabular}

\tikz[overlay]{
	\draw[orangep, thick,->] plot[smooth,tension=.3] coordinates{(Nterm.south) ($(Nterm.south) + (0,-.5cm)$) ($(Ntext.north) + (0,.5cm)$)
	 (Ntext.north)};
	\draw[orangep, thick,->] plot[smooth,tension=.3] coordinates{(Bterm.south) ($(Bterm.south) + (0,-.7cm)$) ($(Btext.north) + (0,.5cm)$)
		(Btext.north)};
}

\begin{itemize}
\item Constants ($\psi,\zeta,\xi$) depend only on \hlg{step size $\alpha$} and \hlg{epoch size $m$}
\item Theory dictates \hlr{very conservative} meta-parameters ($\alpha,m,N,B)$  to guarantee convergence
\end{itemize}
}

\headerbox{Algorithm}{name=algo,column=1,span=1,row=1,below=svrpg}{
\noindent
\small
%\begin{minipage}[t]{.7\textwidth}
\textbf{For} $s = 1,\ldots$
\vspace*{-.2cm}
\begin{rightbrace2}
	Sample $N$ trajectories using $\wt{\theta}$\\
	Compute FG $=\wh{\nabla}_N J(\wt{\theta})$\\
	\textbf{For} $t = 1, \ldots, m$
	\vspace*{-.15cm}
	\begin{rightbrace1}
	Sample $B$ trajectories using $\theta$\\
	Compute SG $=\wh{\nabla}_B J(\theta)$\\
	Compute correction $=\omega(\theta, \wt{\theta})\wh{\nabla}_B J(\wt{\theta})$\\
	Update $\theta\gets\theta+\alpha\gradBlack{\theta}$
	\end{rightbrace1}
	\vspace*{-.15cm}
	\hspace*{-.5cm}Update $\wt{\theta}\gets\theta$
\end{rightbrace2}
\vspace*{-.2cm}
}

\headerbox{Heuristics}{name=heuristics,column=3,span=1,row=0}{
	\begin{itemize}
		\item Adaptive step size
		\item Adaptive epoch size
		\item Normalized Importance Weighting
		\item Critic (baseline)
	\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Empirical Results}{name=emp,column=3,row=1,span=1,below=heuristics}{
	Direi che ci stanno 2 grafici, ma devo pensare a quali mettere

@@

\headerbox{References}{name=ref,column=1,row=2,span=1,below=algo,above=bottom}{
        \tiny
\bibliographystyle{plainnat}
\begingroup
\renewcommand{\section}[2]{}%
\bibliography{poster.bib}
\endgroup
}
